\chapter*{Acknowledgment}
\addcontentsline{toc}{chapter}{Acknowledgment}

\par I'd like to start by thanking my advisor, Dr. Eric Jankowski. I came into Dr. Jankowski’s lab in quite an unusual way, being at the end of my 3\textsuperscript{rd} year in the MSE PhD program with years of research under my belt and needing to find a new research lab. Needing to find a new research group with short notice I was rather stressed when I first met with Eric, but after discussing my situation and goals with him I left the meeting feeling calm and much more capable of achieving my goals. This is the kind of environment that Eric fosters in his research group. Thank you, Eric, for always displaying your passion and enthusiasm for our research and creating such a welcoming learning experience. It has been a true privilege to work with you as well as all the excellent researchers that I've crossed paths with in the CME lab. I have gain invaluable experiences and friendships from the CME lab that I will continuously cherish. 
\par I'd also like to thank my first research advisor, Dr. Matt King. Thank you for answering my endless questions and teaching me how to be a researcher. I can't thank the lovely MSMSE administrative staff for supporting me throughout the program enough. Each and every one of you truly goes above and beyond for the students in the MSMSE program and make the program such an enjoyable experience. I would like to give thanks to all of our funding sources. This material is based upon work supported by the National Science Foundation under Grant No. 1653954. 
\par To my family, thank you for believing I could accomplish anything, even when I doubted it myself. To my parents, Ken and Shellie, thank you for doing everything you could to ensure I would accomplish every goal I've ever set. I wouldn't be a quarter of the person I am today without having such strong people in my corner. You both are truly my heroes. To my sister, Emily, thank you for being my role model, support system and overall my best friend. I love you all more than word can describe. To Joel, thank you for loving and supporting me through every up and down this journey has had to offer. I couldn't ask for a better partner in this life. 


%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "BSUmain"
%%% End: 
